\documentclass[letterpaper]{article}
\usepackage{enumitem}

\title{Constitution for the Miami University Sport Parachute Club}
\date{October 4, 1972}
\author{Philip Lura}

\newenvironment{sectionlist}{
    \begin{enumerate}[label=\bfseries Section \arabic*.]
}{\end{enumerate}}

\newcounter{articlecount}
\setcounter{articlecount}{1}

\newcommand\article[1]{
	\begin{center}
	\Large{\textbf{ARTICLE \Roman{articlecount} -- #1}}
	\end{center}
	\stepcounter{articlecount}
}


\begin{document}

\maketitle

\article{Name}

The Name of this organization shall be the Miami University Sport
Parachute Club.

\article{Objectives}

\begin{sectionlist}

\item The furthering of competitive sport relationships with
  organizations within and without the collegiate sphere of
  activities.

\item The promotion of greater interest in sport parachuting and the
  diffusion of knowledge concerning this sport.

\item To provide an opportunity for students and other persons to gain
  experience and find recreation in sport parachuting.

\end{sectionlist}

\article{Membership}

\begin{sectionlist}

\item Membership in the club is open to men and women of Miami
  University, subject to the approval of the Club officers.

\item Members must be eighteen (18) years of age or over, or must be
  sixteen (16) years of age or over and have obtained written
  permission to perform parachute jumps from both parents, if living,
  or guardian.

\item A properly signed legal waiver absolving the club from legal
  responsibility for damage to his own person, other persons or
  property resulting from his own actions will be permitted to perform
  a parachute jump.

\item Each member must keep himself constantly familiar with all state
  and other regulations concerning sport parachuting, and must obey
  these regulations. Each member must further observe and obey all
  regulations imposed upon the Club by the officers of the Club. Club
  safety regulations are especially important and must be obeyed
  implicitly at all times. Club officers may, by special meeting
  suspend or revoke an individual's membership for infringement of the
  regulations at any time.

\item No member of this Club may enter into pre-jump training before
  signing his or her name to a statement which stipulates that he or
  she has read and understands a copy of this constitution.

\end{sectionlist}

\article{Officers}

\begin{sectionlist}

\item \underline{A Team Captain and Safety Officer.} The duties of
  this officer will be: the supervision of the team's method of
  participating in competition parachuting; the observation of each
  member's progress; the strict enforcement of the parachuting
  regulations established by the Club, by the laws of the state, the
  Federal Aviation Agency, and by the United States Parachute
  Association. The safety Officer must obtain USPA appointment.

\item \underline{A Secretary.} The duties of the Secretary will be to
  maintain communications between the Team Captain and the Club
  members; to establish contact with other parachuting clubs; to
  maintain the Club's intelligence concerning the laws and regulations
  governing the conduct of men permitted to parachute; to be
  responsible for the efficient and orderly conduct of Club meetings.

\item \underline{A Treasurer.} The duties of the Treasurer will be to
  handle the regular financial matters connected with his office.

\item All officers are eligible to parachute if they have met the
  regular requirements.

\item The election of the above named officers shall occur during the
  first Club meeting after the Spring Vacation. A simple majority vote
  of the members present being sufficient, provided that all members
  are notified at least two (2) days in advance of the time and place
  of such as election.

\end{sectionlist}

\article{Delegation of Authority}

\begin{sectionlist}

\item By an affirmative vote of two-thirds (2/3) of the members,
  complete authority for the operation of the Club may be delegated to
  a designated individual, for a designated period of time. At the
  expiration of this period, the designated individual will render a
  complete report to the Club in writing.

\end{sectionlist}

\article{Amendments}

\begin{sectionlist}

\item Amendments to this constitution can be made at any time by the
  affirmative vote of two-thirds (2/3) of the members.

\end{sectionlist}

\bigskip

\begin{center}
  Adopted: 9/27/72
\end{center}

\end{document}
